Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-07-14 paper/paper.tex
coments removed

The low p-values are illustrated by the results shown in Figure \ref{multiphaseresults}.
Left column shows the difference between the integrated distributions
of the full sample (2500 input models) and the $1\%$ models with the lowest
$\chi^2/d.o.f.$, where we use the total number of degrees of freedom,
$d.o.f.=104$. 
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
\mg{These errors seem still pretty small to me. You obtained these via a Fisher matrix of a parabolic fit, right? How good was the fit? Are the off-diagonal elements included?}
\jefr{The small uncertainty only says that the increase in
  $\chi^2/dof$ is very steep as you vary a parameter. I don't think you can get larger errors
  with the available data. Simple inspection of Figure 2 shows
  that the errors will be small with the data we have. The
  paremeter uncertainty roughly corresponds to the width of the parabola
  when there is a difference of $\chi^2/dof\sim 1$ from the minimum. In the data we
  have a huge jump of $\chi^2/dof$ of $\sim 5$ between the minimum
  and the nearest data point. }

@@

\jefr{I find this paragraph confusing. Discussing an hypotetical case where
all parameters are important undermines the explanation of our concrete case
where only some parameters matter more. Probably we can remove it}.
{\bf However, larger values of $f_{\rm cl}$ -- outside the here considered parameter range -- would re-introduce
additional radiative transfer effects and thus increase the number of
relevant parameters \citep[see ][for details]{2017arXiv170406278G}.   
This means that even  
if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, the rest of parameters
affect the line profile at a level that cannot be neglected.}

{\bf As a test we run a small set of $100$ additional radiative
transfer simulations with random values for all parameters, except for
$\sigma_{\rm cl}$, $P_{\rm cl}$ which are kept within the derived $3\sigma$
constraints. We find that $30$ models show $\chi^2/d.o.f.<35$.
That is, we have a $30\%$ chance to find good models, which is
significanty higher than the lower $1\%$ success rate if the
parameters were unconstrained.  }
\mg{Is $1\sigma$ correct?}\jefr{I checked and only $\sigma_{cl}$ and
  $P_{cl}$ were run within $3\sigma$. All the other parameters,
  including $v_{\infty}$, were
  unconstrained. Should we mention this test given that we didn't run
  with a constrain on $v_{\infty}$?}

@@

Which model has more
chances to be correct?  
We argue that that the rotation model should be discarded by
considering that the prefered rotational velocity of $V_{m}\sim350$
\kms\ is of the same order as the largest rotational velocity of giant
disc galaxies that have two orders of magnitude more baryonic mass
than \tol\ \citep{2015MNRAS.448.1767C}.  
\mg{I am confused -- are much lower rotational
  velocities not exclude by the priors used?}\jefr{Yes, they are
  discarded, but here we are talking about the most likely value of
  350 km/s.}

@@

We divide
the results in two classes: low $\chi^2/d.o.f.<35$ and high
$\chi^2/d.o.f.>35$, that is the limit that divides the best $1\%$ of
the models from the rest. \mg{Why was $35$ chosen as a boundary?}\jefr{We
  chose $35$ to match the cut that we used to make the  integrated
  probability distributions. However the nuber itself is
  arbitrary to have the $1\%$ of the initial number of models. 
Ideally we should only chose models with $\chi^/dof$
  higher by $2$ than the lowest $\chi^2/dof$, but we don't have any
  models in that range.}
The algorithm uses $500$ trees for the classification and a
maximum of $3$ depth levels. 
To check for stability we repeat the computation $10$ times by
randomly subsampling the input data to use $80\%$ of the data as
the training set.

@@

{\bf Furthermore, considering the sparse sampling of parameter space and the results
from the random forest classifier, it is safer to consider that
the best values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm
  cl}$ are actually lower/upper/lower bounds, respectively.}
\mg{This is interesting. Why do you think that? Could we use that to
  increase the quoted errors? I am worried that the referee will
  complain about the small errors.} \jefr{The referee didn't complain
  about the small errors. And now that I see this with a bit more of
  perspective, the tree classification always work with 'larger
  than/less than' dualities. It would be unfair/unjustified to use that to justify
our results as a lower bound. I suggest we remove this paragraph.}

>>>>

The low p-values are illustrated by the results shown in Figure \ref{multiphaseresults}.
Left column shows the difference between the integrated distributions
of the full sample (2500 input models) and the $1\%$ models with the lowest
$\chi^2/d.o.f.$, where we use the total number of degrees of freedom,
$d.o.f.=104$. 
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.

@@

@@

Which model has more
chances to be correct?  
We argue that that the rotation model should be discarded by
considering that the prefered rotational velocity of $V_{m}\sim350$
\kms\ is of the same order as the largest rotational velocity of giant
disc galaxies that have two orders of magnitude more baryonic mass
than \tol\ \citep{2015MNRAS.448.1767C}.

@@

We divide
the results in two classes: low $\chi^2/d.o.f.<35$ and high
$\chi^2/d.o.f.>35$, that is the limit that divides the best $1\%$ of
the models from the rest. 
The algorithm uses $500$ trees for the classification and a
maximum of $3$ depth levels. 
To check for stability we repeat the computation $10$ times by
randomly subsampling the input data to use $80\%$ of the data as
the training set.

@@
